Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-03-01 paper.tex
update

The paper is organized as follows. 
Section \ref{background} reviews the background.

@@

In this section, we first describe the target language we will
analyze and a concrete CESK machine as operational semantics for it.
Then we review some recent works in control-flow analysis for
higher-order languages:
1) abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines, and
2) the precise call/return match problem in control-flow analysis and its existing solutions.
We will show in section 3 that the abstracting abstract machines form the basis of our transformations,
and call/return match is obtained during transformation.

@@

Traditionally, continuation-passing style (CPS) is a popular intermediate representation
for analyzing functional programs because of it exposes control transfer explicitly
and simplifies the analysis \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007}.
Here, we choose to use administrative normal form (ANF) which is a direct-style intermediate representation 
as target for clarity but without losing simplicity and generality.
Although we just show the core calculus language, but it can be easily extended
to support recursive bindings, conditionals, primitive types and operations on primitive types.
The transformations we will show in the rest of this paper
also work on abstract machines for plain, direct-style $\lambda$-calculus languages.
TODO: add letrec?

>>>>

The paper is organized as follows.

In section \ref{background}, we first describe the target language we will
analyze and a concrete CESK machine as operational semantics for it.
Then we review abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines.

@@

2) the precise call/return match problem in control-flow analysis and its existing solutions.

@@

Traditionally, continuation-passing style (CPS) is a popular intermediate representation
for analyzing functional programs because of it exposes control transfer explicitly
and simplifies the analysis \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007}.
Here, we choose to use administrative normal form (ANF) which is a direct-style intermediate representation 
as target for clarity but without losing simplicity and generality.
Although we just show the core calculus language, but it can be easily extended
to support recursive bindings (such as $letrec$), conditionals, primitive types and 
operations on primitive types. These cases would be trival or simple, so we omit them
in the paper.
The transformations we will show in the rest of this paper
also work on abstract machines for plain, direct-style $\lambda$-calculus languages.
TODO: add letrec?
